\newpage
\subsubsection*{Question 5}
\noindent[15 pts] Suppose $L$ is a regular language. Use the closure properties of regular languages
to show that each of the following languages is regular as well.
\begin{enumerate}[label={(\alph*)}]
    \item $\{uv : u \in L$ and $|v| = 2 \}$
    \item $\{ uv : u \in L$ and $v \in L^R \}$
    \item $\{ u : u \in L$ and $u^R \in L\}$
\end{enumerate}

\subsection*{Answer}

\begin{enumerate}[label={(\alph*)}]
    \item 
        \begin{proof}
            First, we have that $|v| = 2$. $v$ is therefore a finite language, meaning it is necessarily regular. We are also told that $u \in L$ and $L$ is regular, meaning that $u$ is regular as well.\\
            The concatenation closure property states that regular languages are closed under concatenation. Knowing that and since $u$ and $v$ are regular languages, we know that $uv$ is necessarily a regular language.
        \end{proof}
    \item
        \begin{proof}
            First, we know that $u$ is a regular language since we are told that $L$ is a regular language and that $u \in L$.\\
            Also, since regular languages are closed under reversal, we know that if $L$ is regular, $L^R$ is also a regular language. Hence, since $v \in L^R$, $v$ is also a regular language.\\
            The concatenation closure property states that regular languages are closed under concatenation. Knowing that and since $u$ and $v$ are regular languages, we know that $uv$ is necessarily a regular language.
        \end{proof}
    \item 
        \begin{proof}
            We are told that $L$ is a regular language hence since $u \in L$, $u$ is also a regular language.
        \end{proof}
\end{enumerate}